\section{VMF Semantics}

\subsection{VMF Syntax \& Dynamics}

\paragraph{Program syntax.}
For economy of both implementation and reasoning, the syntax of VMF
programs is directly insipired by that of the Call-by-Push-Value
(CPBV) syntax and evaluation strategy~\cite{CBPV}.
%
CBPV is similar to CBV, except that unlike CBV, CBPV neatly separates
the concept of a thunked computation from that of a lambda
abstraction.
%
Like other administrative normal forms, CPBV also imposes a separation
of values and computations, in terms of syntax and semantics.
%
Computations that eliminate values have value sub-terms.
%
In contrast to computation forms, value forms consist of (passive,
non-doing) data types; specifically, here we consider variables
(ranging over previously-defined values), primitives (viz., numbers
and strings), records of values, store locations, open thunks that
suspend a computation term as a value~($\ottkw{othunk} \, \ottnt{e}$) and thunks
closed by an environment~($\ottkw{thunk} \, \rho \, \ottnt{e}$).

Unlike values, computations consist of program terms that actively
\emph{do things}, and for which the VM defines operational steps. For
instance, field projection from a record value is a computation, since
it eliminates a value (viz., the record that contains the projected
field) and introduces a new one.
%
Though CBV treats lambdas as values, the distinctive quirk of CBPV is
that function abstraction is a computation (not a value) and that it
interacts with function applications via an ambient stack (hence,
``call-by-\emph{push}-value''):
%
Function application~$\ottnt{e} \, \ottnt{v}$ uses a function abstraction by pushing
an argument value~$v$ on this ambient stack and then running the
function body~$e$.
%
Lambdas~$ \lambda  x .  \ottnt{e} $ abstract over a variable~$x$ by popping a value
for~$x$ from this ambient stack.
%
Compared with CBV, the presence of this ambient stack streamlines the
expression of currying.
%
Specifically, CBPV avoids the need for creating closures that
represent the partially-applied lambdas in the curried series.
%
Below, we will augment these (standard) computations and values with
computations over simple databases.

\paragraph{VM State syntax.}

\paragraph{VM Dynamics.}


\section{Gradual Typing for Simple Databases}


\paragraph{Library primitives: Syntax \& Dynamics.}

